\documentclass{article}

\usepackage[top=2.54cm, bottom=2.54cm, right=2.54cm, left=2.54cm]{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{url}
\usepackage{setspace}

\renewcommand{\rmdefault}{phv}
\onehalfspacing

\title{} 
\author{
    Entry Name: \textbf{``LCEE-MC3''}\\
    \textbf{VAST Challenge 2019}\\
    \textbf{\underline{Mini-Challenge 3}}}
\date{}

\begin{document}
%\maketitle

\begin{center}
Entry Name: \textbf{``LCEE-MC3''}\\
\textbf{VAST Challenge 2019}\\
\textbf{\underline{Mini-Challenge 3}}
\end{center}

\noindent
\textbf{Team Members:}\\
Ana Larissa Dias, Federal University of Par\'{a}, \href{mailto:larissa.engcomp@gmail.com}  {\texttt{larissa.engcomp@gmail.com}}   \\
Cassio Batista,   Federal University of Par\'{a}, \href{mailto:cassio.batista.13@gmail.com}{\texttt{cassio.batista.13@gmail.com}} \\
Edwin Rueda,      Federal University of Par\'{a}, \href{mailto:ejrueda95g@gmail.com}       {\texttt{ejrueda95g@gmail.com}}        \\
Erick Campos,     Federal University of Par\'{a}, \href{mailto:erick.c.modesto@gmail.com}  {\texttt{erick.c.modesto@gmail.com}}   \\

\noindent
\textbf{Student Team:} YES \\

\noindent
\textbf{Tools Used:}
\begin{itemize}
    \item \href{https://www.python.org/downloads/}               {Python}           (v3.5.3)
    \item \href{https://bokeh.pydata.org/en/latest/}             {Bokeh}            (v1.2.0)
    \item \href{https://www.nltk.org/}                           {NLTK}             (v3.4.1)
    \item \href{https://textblob.readthedocs.io/}                {TextBlob}         (v0.15.3)
    \item \href{https://www.numpy.org/}                          {NumPy}            (v1.16.0)
    \item \href{https://pandas.pydata.org/}                      {pandas}           (v0.24.2)
    \item \href{https://matplotlib.org/}                         {Matplotlib}       (v3.0.2)
    \item \href{https://github.com/amueller/word_cloud}          {word\_cloud}      (v1.5.0)
    \item \href{https://scikit-learn.org/stable/}                {scikit-learn}     (v0.20.2)
    \item \href{https://nodejs.org/en/download/}                 {Node.js}          (v10.16.0)
    \item \href{https://www.libreoffice.org/}                    {LibreOffice Calc} (v5.2.7.2)
    \item \href{http://man7.org/linux/man-pages/man1/grep.1.html}{grep}             (v2.27)
\end{itemize}

\noindent
\textbf{Approximately how many hours were spent working on this submission in
total?} 114 hours \\

\noindent
\textbf{May we post your submission in the Visual Analytics Benchmark Repository
after VAST Challenge 2019 is complete?} YES \\

\noindent
\textbf{Video:} \url{https://youtube.com/?v=vaietefuder}\\

%\newpage
\noindent
\textbf{Questions} \\
\footnotesize{\textcolor{gray}{The City has been using Y*INT to communicate with
its citizens, even post-earthquake. However, City officials needs additional
information to determine the best way to allocate emergency resources across all
neighborhoods of St. Himark. Your task, using your visual analytics on the
community Y*INT data, is to determine the types of problems that are occurring
across the St.  Himark. Then, advise the City on how to prioritize the
distribution of resources. Keep in mind that not all sources on Y*INT are
reliable, and that priorities may change over time as the state of neighborhoods
also changes.}}

\begin{enumerate}
    \item \textcolor{gray}{Using  visual analytics, characterize conditions
        across the city and recommend how resources should be allocated at 5
        hours and 30 hours after the earthquake. Include evidence from the data
        to support these recommendations. Consider how to allocate resources
        such as road crews, sewer repair crews, power, and rescue teams. 1000
        words, 12 images.}

    \input{secs/question_1}
    \newpage

    \item \textcolor{gray}{Identify at least 3 times when conditions change in
        a way that warrants a re-allocation of city resources. What were the
        conditions before and after the inflection point? What locations were
        affected? Which resources are involved? Limit your response to 1000
        words and 10 images.}

    \input{secs/question_2}

    \item \textcolor{gray}{Take the pulse of the community.  How has the
        earthquake affected life in St. Himark? What is the community
        experiencing outside the realm of the first two questions? Show decision
        makers summary information and relevant/characteristic examples. Limit
        your response to 800 words and 8 images.}

    \input{secs/question_3}

    \item \textcolor{gray}{The data for this challenge can be analyzed either as
        a static collection or as a dynamic stream of data, as it would occur in
        a real emergency. Describe how you analyzed the data --- as a static
        collection or a stream. How do you think this choice affected your
        analysis? Limit your response to 200 words and 3 images.}

    \input{secs/question_4}
\end{enumerate}
\end{document}
